---
title: "ps_4"
author: "Evelyn Cai"
date: "February 26, 2019"
output: html_document
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(dplyr)
library(tidyverse)
library(devtools)
library(gt)
```

``` {r Question 1 madlibs}
# Read in CSV file
x <- read_csv(file = "ps_4_elections-poll-nc09-3.csv")

# Create separate variable to store value of number of Republican supporters
rep_number <- x %>% filter(response == "Rep") %>%
  count()
# Create separate variable to store the value of the number of Republican supporters
und_number <- x %>% filter(response == "Und") %>%
  count()
  
# Question 3
rep_timestamp <- x %>%
  # Filter for only Republican favoring participants
  filter(response == "Rep") %>%
  # Only select for the one thing we are interested in (timestamp)
  select(timestamp) %>%
  # Arrange from earliest to latest time
  arrange(timestamp) %>%
  # Take the top result
  slice(1) %>%
  # Turn the tibble into a vector for the strptime() function
  pull(timestamp) %>%
  strptime(format = "%Y-%m-%d %H:%M:%S")
# Same process for the Democrat-favoring participants
dem_timestamp <- x %>%
  filter(response == "Dem") %>%
  select(timestamp) %>%
  arrange(timestamp) %>%
  slice(1) %>%
  pull(timestamp) %>%
  strptime(format = "%Y-%m-%d %H:%M:%S")

```
## Question 1

There were `r x %>% filter(response == "Dem") %>% count()` respondents who supported the Democratic candidate.

There were `r x %>% summarize(difference = rep_number - und_number)` more respondents who favored the Republican candidate than who were Undecided.

There are two gender variables (`gender` and `gender_combined`). There are `r ` individuals for whom these variables have different values.

There are `r ` respondents listed as “White” under race_eth who are not listed as “White” under file_race_black.

The first response of Rep came `r difftime(rep_timestamp, dem_timestamp, units = "mins") %>% round(digits = 0)` minutes (rounded to the nearest minute) before the first response of Dem.


## Question 2
```{r Question 2 Chart}
x %>%
  # Select the variables that are being used/ summarized/ mutated/ displayed in the chart
  select(response, race_eth, final_weight) %>%
  # Filter out refused responses to the ethnicity/race question
  filter(race_eth != "[DO NOT READ] Don't know/Refused") %>%
  # Mutate both filters and changes the order of the races in the display
  mutate(race_eth = fct_relevel(race_eth, "White", "Black", 
                                "Hispanic", "Asian", "Other")) %>%
  # Associate race and party through group_by function
  group_by(race_eth, response) %>%
  # Find the total number of voters out of those who responded Dem, Rep, and Und
  summarize(total = sum(final_weight)) %>%
  # Spread out the 'response' horizontally, and set fill = 0 so that 0 is the default value for missing values instead of NA
  spread(key = response, value = total, fill = 0) %>%
  # Create a total value in which every 'response' is counted, even third parties, and calculate the proportion of voters of that race for that particular political party
  mutate(All = Dem + Rep + Und + `3`,
         Dem = Dem / All,
         Rep = Rep / All,
         Und = Und / All) %>%
  # Remove 'All' and '`3`' column from chart
  select(-All, -`3`) %>%
  # Make it so that each cell in the chart is a particular race with a particular party, instead of five different groups by race
  ungroup() %>%
  # Create an attractive chart using gt:)
  gt() %>%
  # Title the chart to reflect the data we're analyzing
  tab_header(
    title = "Polling Results in North Carolina’s 9th Congressional District") %>%
  # Rename the column variables
  cols_label(
    Dem = "DEM.",
    Rep = "REP.",
    Und = "UND.",
    race_eth = "") %>%
  # Add a percent sign to the end of each number and round to the nearest whole number
  fmt_percent(columns = vars(Dem, Rep, Und),
              decimals = 0) %>%
  # Change any 0s back to NA
  na_if(0) %>%
  # Change NA to a dash
  fmt_missing(columns = vars(Und), rows = 4)
```
